---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PRFgrowth

<!-- badges: start -->
<!-- badges: end -->

Implementation of age-independent height growth and height growth-rate models for mixedwood forest in the Petawawa Research Forest.  

## Installation

You can install the development version of PRFgrowth like so:

``` r
install.packages("devtools")
devtools::install_github("jgriofrio/PRFgrowth")
library(PRFgrowth)
```

## Example

The functions `Hgrowth` and `HGindex` return the estimate of the height growth and growth rate index at reference height for a given period length, respectively.

```{r example}
library(PRFgrowth)
## basic example code
```


##   References


Riofrío, J., White, J.C., Tompalski, P., Coops, N.C., Wulder, M.A., 2022. Harmonizing multi-temporal airborne laser scanning point clouds to derive periodic annual height increments in temperate mixedwood forests. Can. J. For. Res. 52, 1334–1352.

Riofrío, J., White, J.C., Tompalski, P., Coops, N.C., Wulder, M.A., 2023. Modelling height growth of temparate mixedwood forests using an age-independent apporach and multiu-temporal airborne laser scanning data .


